\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,booktabs,longtable}
\usepackage[hidelinks]{hyperref}
\hypersetup{pdftitle={Supplementary Materials (V4): From Material Turnover to Causal Memory},
pdfauthor={Autonomous research agent (see AI-authorship disclosure)}}
\title{\textbf{Supplementary Materials (V4)}\\ \large From Material Turnover to Causal Memory:
Organizational Continuity in a Simulated Droplet}
\author{Autonomous research agent (see AI-authorship disclosure in the main text)}
\date{July 2026}
\begin{document}\maketitle

\noindent\textbf{Scope of this revision (V4).} All longitudinal held--out numbers are now the canonical outputs of the committed \texttt{reproduction/} package (\texttt{python -m reproduction.primary}); the historical, non--reproducible values are documented in \texttt{HEADLINE\_NUMBER\_ERRATUM.md}. \textbf{(V3 scope note, retained.)} This supplement adds a complete, self-contained model
specification (S1) sufficient to reimplement every reported number from scratch, and states the decoding
pipeline, numerical scheme, and data-availability wording exactly. Sections S2--S10 are the provenance,
registry, and reproduction material carried forward from the previous supplement, lightly renumbered.

\section{S1. Complete model specification}
All fields live on a periodic $64\times64$ square lattice, integrated by explicit forward Euler with
time step $\mathrm{d}t=0.1$. The periodic five--point Laplacian is
\begin{equation}
(\Delta X)_{ij}=X_{i+1,j}+X_{i-1,j}+X_{i,j+1}+X_{i,j-1}-4X_{ij}.
\end{equation}
The engine is the frozen scaffold blob \texttt{7c91b91}; the memory field is the frozen IOM--00 writing law
(\texttt{dc04f5d}) with the two orthogonal readouts of MCM--00. With $\lambda_+=\lambda_-=0$ the base fields
$(\rho,U,V,c,N)$ evolve bit--identically to the memory--free scaffold.

\subsection*{S1.1 State variables}
$\rho$ (scaffold density); $U=\rho u$, $V=\rho v$ (extensive internal bistable species, concentrations
$u,v$); $c$ (shared attractant); $N$ (nutrient); $C$ (passive cohort tracer, $\sum_c C=\rho$ exactly);
$M_k=\rho\, m_k$ for $k\in\{1,2\}$ (extensive memory, intensive $m_k\in[-1,1]$).

\subsection*{S1.2 Cohesion: chemotactic advection with volume exclusion}
Per axis, for the forward neighbour ($\rho^+=\mathrm{roll}(\rho)$, $c^+=\mathrm{roll}(c)$,
$\mathrm{d}c=c^+-c$) the face flux is upwind in $\mathrm{d}c$:
\begin{equation}
\chi=\frac{\chi_0}{1+\big(\tfrac{1}{2}(c+c^+)/c_{\mathrm{sat}}\big)^2},\quad
J=\underbrace{\chi\,\mathrm{d}c\,\rho_{\uparrow}\Big(1-\tfrac{\rho_{\downarrow}}{\rho_{\max}}\Big)_{\!+}}_{\text{advection}}
\;-\;\underbrace{D_\rho(\rho^+-\rho)}_{\text{diffusion}},
\end{equation}
where $\rho_\uparrow=\rho$, $\rho_\downarrow=\rho^+$ if $\mathrm{d}c>0$, else swapped. The density update is the
flux divergence $\partial_t\rho=-\sum_{\text{axes}}(J-\mathrm{roll}(J,1))$. The extensive carriers
$U,V,C,M_k$ advect with the same flux using donor--cell intensive fractions ($U/\rho$, $V/\rho$, $C/\rho$,
$M_k/\rho$).

\subsection*{S1.3 Growth (nutrient uptake), death}
With $\sigma=(u-v)/(u+v)$, $q=(1-\rho/\rho_{\max})_+$, and dose readout $m_+=\tanh(m_1+m_2)$:
\begin{align}
g&=\mathrm{d}t\;g_0\,\rho\,N\,q\,(1+\beta\sigma)\,(1+\lambda_+ m_+),\qquad g\leftarrow\mathrm{clip}(g,0,N),\\
N&\leftarrow N-g,\quad \rho\leftarrow\rho+g,\quad U\leftarrow U+gu,\quad V\leftarrow V+gv,\quad M_k\leftarrow M_k+g\,m_k.
\end{align}
New mass inherits the local internal state and local memory. The uptake observable is $\mathrm{uptake}=g$.
Death is homogeneous, $X\leftarrow(1-\mathrm{d}t\,k)X$ for $X\in\{\rho,U,V,C,M_k\}$, so intensive
concentrations and memory are invariant under pure turnover.

\subsection*{S1.4 Internal bistable identity (confined to the scaffold)}
Where $\rho>10^{-4}$ and $a>0$, on concentrations:
\begin{equation}
\dot u=\frac{a}{1+(v/K)^2}-u,\quad \dot v=\frac{a}{1+(u/K)^2}-v,\qquad
u\leftarrow u+\mathrm{d}t(\tau\dot u+D_{\mathrm{int}}\Delta u),
\end{equation}
(analogously $v$), then clipped to $\ge0$ and re--made extensive $U=\rho u,\,V=\rho v$. This network never
enters $\chi$, $c$, or any cohesive term.

\subsection*{S1.5 Memory writing (frozen) and the two readouts}
Let $\bar{\mathrm{uptake}}$ be the entity--mean uptake. The single local experience signal is
\begin{equation}
\Psi=\tanh\!\big(k_{\exp}(N-c)+k_{\mathrm{up}}(\mathrm{uptake}-\bar{\mathrm{uptake}})\big).
\end{equation}
Each intensive component, where $\rho>10^{-4}$, obeys write / two--timescale forgetting / templating /
diffusion:
\begin{equation}
m_k\leftarrow\mathrm{clip}\!\Big(m_k+\mathrm{d}t\big[\eta_w\Psi-\eta_{d,k}m_k+\eta_t(\widetilde{m_k}-m_k)+D_m\Delta m_k\big],\,-1,1\Big),
\label{eq:mem}
\end{equation}
with $\eta_{d,1}$ (fast) and $\eta_{d,2}$ (slow), and the templating reference
$\widetilde{X}=\tfrac14(X_{i\pm1,j}+X_{i,j\pm1})$ (periodic four--neighbour mean). Readouts:
\begin{align}
\text{dose (channel 1):}\ &m_+=\tanh(m_1+m_2)\ \to\ \text{uptake gain }(1+\lambda_+m_+)\ \text{[in S1.3]},\\
\text{order (channel 2):}\ &m_-=\tanh(m_1-m_2)\ \to\ c\text{ production }(1+\lambda_-m_-).
\end{align}
The attractant and nutrient close the system:
\begin{equation}
c\leftarrow c+\mathrm{d}t\big(D_c\Delta c+s\,\rho\,(1+\lambda_-m_-)-\delta c\big),\quad
N\leftarrow N+\mathrm{d}t\big(D_N\Delta N+F(N_0-N)\big).
\end{equation}

\subsection*{S1.6 Frozen parameters}
Scaffold (blob \texttt{7c91b91}): $\chi_0=9.5$, $D_\rho=0.07778$, $D_c=0.68$, $s=0.2$, $\delta=0.06909$,
$g_0=0.06154$, $k=0.02588$, $F=0.02421$, $D_N=0.5$, $N_0=1.0$, $\rho_{\max}=c_{\mathrm{sat}}=1.0$, $a=2.0$,
$K=0.5$, $D_{\mathrm{int}}=0.008$, $\tau=0.20$, $\beta=0.6$, lattice $64$, $\mathrm{d}t=0.1$.
Memory (selected candidate \textbf{C1c}, frozen \texttt{FREEZE\_C1c.json}): $\eta_w=0.015$,
$\eta_{d,1}=0.35$, $\eta_{d,2}=0.006$, $\eta_t=0.010$, $D_m=0.010$, $\lambda_+=0.25$, $\lambda_-=0.15$,
$k_{\exp}=1.0$, $k_{\mathrm{up}}=1.0$, $n_{\mathrm{comp}}=2$. (C1c is the de--saturated writing correction of
the IOM--00 default $\eta_w=0.05,\eta_{d,1}=0.03,k_{\exp}=2.0$.)

\subsection*{S1.7 History coordinates}
Each history applies an early and a late environmental drive of amplitudes $a_{\mathrm{early}},a_{\mathrm{late}}$.
The two decoded coordinates are the cumulative dose $h_1=a_{\mathrm{early}}+a_{\mathrm{late}}$ (global, non--individuating)
and the temporal order / asymmetry $h_2=a_{\mathrm{late}}-a_{\mathrm{early}}$.

\subsection*{S1.8 Entity detection}
Connected components (periodic 4--connectivity) of the mask $\{\rho>0.30\,\rho_{\max}\}$; components with
$\ge12$ cells are entities. Centroids use the periodic circular--mean estimator; radius of gyration and all
phenotype statistics are computed on the entity cells with $\rho$--weighting.

\subsection*{S1.9 Decoding pipeline (how every $R^2$ is obtained)}
Memory feature vector per entity: for each component $m_k$ over the entity cells, the five order statistics
$[\text{mean},\text{std},P_{10},P_{50},P_{90}]$, concatenated over $k=1,2$ to a \textbf{10--D} vector
(entities with $<4$ cells are undefined and censored). Decoder: \textbf{ridge regression},
regularisation $\lambda=1.0$, evaluated by \textbf{grouped leave--one--history--out} cross--validation (the
held--out fold is an entire history class, never a single entity, to prevent leakage). Uncertainty:
donor--level \textbf{percentile bootstrap}, $n_{\mathrm{boot}}=3000$, resampling the grouping unit (history/seed),
reported as $95\%$ CIs. Longitudinal tracking: periodic mask--overlap matching, overlap threshold
$\theta=0.1$, evaluated \textbf{every 5 steps}, censored on track loss; the tracker never reads
$h_1,h_2,M$, or any label. Turnover fraction $M$ is the surviving mass fraction of the original cohort field.

\section{S2. Protocol history (the nine--experiment ladder)}
Each experiment below was specified by a protocol committed \emph{before} its prospective family was
generated and executed once (see the provenance table in the main text for protocol / commit / freeze /
execution timestamps and hashes). HMC (material continuity): snapshot nearly sufficient, no strong
history--specific hidden persistence. HSI (hidden state): generic causal attractor, not individuating
(AUC $0.3$--$0.4$). IOM--00: designed two--component memory; causal, erasable, transplantable; readout
$\approx$1--D. MCM--00: $m_-\!\to$attractant makes order readable ($\sim$70/73$\times$ ablation collapse).
WD--01 Phase B: grouped--evaluation correction ($0.57\to0.19$); rank $\approx$1. Phase C: de--saturated
writing (C1c); two storage coordinates at rest, causal response $\approx$1--D. SMC--01: $h_2$ frame--free
dispersion; a turnover collapse later corrected. DMM--01: correction --- inter--family variance, not
smoothing/dilution; underpowered. H2--CERT--01: sealed kill--switch, $h_2$ canonical point $-0.24$ at $M\approx0.19$
with a CI spanning the $0.50$ threshold (retention \emph{not established}). TCA--01: tracker--continuity
audit; longitudinal re--certification of $h_1$.

\section{S3. Branch / commit registry}
\begin{longtable}{@{}ll@{}}\toprule experiment & result commit\\\midrule
HMC & 25c419a\\ HSI & 709f963\\ IOM--00 & 0ea1250\\ MCM--00 & 5841b9b\\ WD--01 Phase B & 9a39f8c\\
WD--01 Phase C (seal / result) & be08738 / a07b95b\\ SMC--01 (seal / result) & d0f47b6 / 3dc8c35\\
DMM--01 (seal / result) & 5bd46e7 / 49e96ad\\ H2--CERT--01 (seal / result) & 5e1196f / 1f8f789\\
consolidation / observer & 112aace / 6891ef8\\ tracker audit / post--incident & 568af39 / 7afd6e4\\
short--paper V0 / full manuscript & a97909a / (this commit)\\\bottomrule\end{longtable}
Main branch never modified (HEAD f3921a4); nothing pushed (origin/main e17f431).

\section{S4. Sealed prospective family hashes (SHA--256, generated before selection, executed once)}
\begin{longtable}{@{}lll@{}}\toprule experiment & seeds (dev / prospective) & SHA--256\\\midrule
Phase C & 34001--3 / 35001--3 & c6d0cd3c5b82aa122ac7e5649888fbc53ca6faa8db68e2c1b48863e87fb9e202\\
SMC--01 & 36001--3 / 36501--3 & 2d6986fe2499cb52fdc309f5b1867cff56cb04b4bd7884633c4c2a148d5792ef\\
DMM--01 & 37001--3 / 37501--3 & 923d8890ea25ab5a136078486f282ad8e07f4cdbaa125da40ef930f5bb8a00b6\\
H2--CERT & --- / 38501--4 & 4265b98cacb705a7bea56a2e0a5bbe36e10fec3d977e7da6e655037189193fee\\\bottomrule\end{longtable}
Seed families disjoint across experiments (32xxx--38xxx). ``Executed once'' means the prospective family was
run a single time after the protocol freeze; no prospective seed was re--run to obtain a preferred number.

\section{S5. Parameter grids and negative candidates}
Writing--redesign candidates compared at development (Phase C): C0 (frozen baseline), C1a/C1b/C1c
(dynamic--range corrections varying $\eta_w,\eta_{d,1},\eta_{d,2},k_{\exp}$), C2a (distinct write signals).
Development $\min(R^2(h_1),R^2(h_2))$ on family F\_mid: C0 $0.19$, C1a $0.84$, C1b $0.61$, C1c $0.84$,
C2a $0.79$; C1c selected for the highest stored second--dimension ratio ($\sigma_2/\sigma_1=0.229$) at
equal top score, by minimality (a same--signal C1). Maintenance candidates (DMM Phase A, diagnostic only):
templating and diffusion ablations and static memory relaxation all left the $h_2$ decode essentially
unchanged. Negative variants were retained, not discarded.

\section{S6. Gate certificates (machine--readable)}
JSON gate certificates are committed per experiment: \texttt{results/wd01/wd01\_gate\_certificate.json},
\texttt{results/wd01\_phasec/wd01\_phasec\_gate\_certificate.json},
\texttt{results/smc01/smc01\_gate\_certificate.json},
\texttt{results/dmm01/dmm01\_gate\_certificate.json},
\texttt{results/h2cert/h2cert\_gate\_certificate.json}. Each records the preregistered gates and the observed
values, including the gates that were \emph{not} met.

\section{S7. Tracker unit tests (TCA--01)}
(i) Selection audit: the historical convenience rule is $\arg\max$ size, reselected per frame; five hard
switches occurred on seed 38501. (ii) Periodic translation invariance: whole--world shifts (including
boundary--straddling) leave size and memory statistics bit--invariant. (iii) Sensitivity: $h_1$ decodes
$0.91/0.89$ from largest / longitudinal trackers (tracker--independent; canonical pipeline).
(iv) Hold--out: untouched seeds 38502--38504, $36/36$ track survival, $h_1$ deep $R^2=0.89$ CI $[0.84,0.96]$, $h_2$ point $-0.24$ CI $[-0.78,0.32]$ (canonical committed pipeline). Specification: \texttt{docs/audit/TCA\_01\_TRACKER\_SPEC.md}.

\section{S8. Seed--family results ($h_1$ turnover) and the re--audited intervals}
DMM pool and H2--CERT sealed families (historical, non--canonical pipeline; retained for provenance only): DMM pool $h_1$ high across $M=1.00\to0.36$; H2--CERT sealed (4 seeds):
$0.94\to0.93\to0.93$ over $M=1.00\to0.44\to0.21$. Longitudinal hold--out (untouched seeds): initial $R^2=0.78$ CI $[0.56,0.94]$, deep $0.89$ CI $[0.84,0.96]$ --- the paper's primary quantitative result (canonical committed pipeline).
Re--audited comparators (grouped bootstrap, $n_{\mathrm{boot}}=3000$): transplant $h_1$ $0.61$ CI
$[-0.69,0.87]$; in--place $h_1$ $0.50$ CI $[-1.39,0.92]$; memory--inert / erased deterministic $-0.19$;
memory vs.\ size$+$mass $0.93$ vs.\ $0.64$ (CIs overlap); longitudinal $h_2$ deep point $-0.24$ CI $[-0.78,0.32]$ (below $0.50$; \emph{not established}). Full methodology: \texttt{STATISTICAL\_REAUDIT\_V4.md}; canonical pipeline \texttt{reproduction/}.

\section{S9. Reproduction commands and data availability}
Environment: python3, numpy, scipy, matplotlib; \texttt{PYTHONPATH=\$REPO:\$REPO/results/wd01\_phasec}.
Per experiment, resumable runners are committed beside their data:
\texttt{results/wd01/run\_diag.py}; \texttt{results/wd01\_phasec/\{dev\_runner,prosp\_runner,causal\_runner,causal\_inplace\}.py};
\texttt{results/smc01/\{fields\_runner,turnover\_runner,prosp\_storage\}.py};
\texttt{results/dmm01/\{phaseA,pooled,prosp\}.py}; \texttt{results/h2cert/\{pilot,cert\}.py};
the tracker hold--out reruns deterministically from the H2--CERT manifest seeds 38502--38504. Viewer:
\texttt{scripts/observe\_droplet.py --preset story}.
\emph{Data availability.} All raw arrays, JSON certificates, sealed manifests, and figure generators
referenced here are committed to the branch \texttt{paper/organizational-memory-boundaries-01} of the
repository \texttt{emergent-dynamics-lab}; every reported number derives from a file in that commit and no
analysed run was excluded from the reported statistics.

\section{S10. Raw--data and figure registry}
Raw: \texttt{results/\{sc\_mcm,wd01,wd01\_phasec,smc01,dmm01,h2cert,observer\}/*.pkl,*.json}. Figures (paper):
Fig.~1 fig1\_model\_ladder; Fig.~2 fig2\_h1\_causal\_v3 (predicted--vs--observed with bootstrap CI);
Fig.~3 tracked\_3panel; Fig.~3b fig3b\_longitudinal\_certification (primary result);
Fig.~4 fig4\_order\_m\_minus; Fig.~5 phasec\_figure; Fig.~6 h2cert\_figure; Fig.~7 paper\_claim\_ladder
(corrected historical summary). Each figure traces to a committed generator script.
\end{document}
